SiO Molecular Jets around young stars - A numerical perspective

### 2013-07-19 PAPER/ms_final_bv.tex
Changes in paper and rm Python book

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/molcjet_510.png}
 \caption{Fraction of hydrogen species in the run with molecular
   cooling having $\eta$ = 5 and $\beta$ = 10.}
\label{grid}
\end{figure*}

@@

\section{Discussion}
Effects of varying $\beta$, $\eta$\\
Importance of cooling prescriptions\\
RADEX plots ratio of Line intensities???\\
Comparison with Observed results \\
Limitations\\

>>>>

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/molcjet_510.png}
 \caption{Fraction of hydrogen species in the run with molecular
   cooling having $\eta$ = 5 and $\beta$ = 10.}
\label{grid}
\end{figure*}

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
 \caption{SiO emission from different line transitions for the run with molecular
   cooling having $\eta$ = 3 and $\beta$ = 10. }
\label{grid}
\end{figure*}

@@

\section{Discussion}
Effects of varying $\eta$\\
Lower $\eta$ gives better emission.

Importance of cooling prescriptions\\
Bulk of emission comes from cooling instabilities.

Spectra and PV Digrams\\
Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
a signature feature of jet driven molecular outflows.

Comparison with Observed results \\
Different line transition trace different components of SiO
emission. The low level transitions trace the region where the jet
interacts with molecular medium. The clumpy nature in its emission is
from the turbulent nature of its interaction. The higher transitions
trace a much more collimated region along with the terminal shock. 
As seen by Chandler \& Richer 2001 and Hirano 2006.

Limitations\\
